How Slow do my Transient Typechecks Go?

### 2019-08-17 paper.tex
Benchmark section needs revision, need input on this though.
Signed-off-by: Stefan Marr <git@stefan-marr.de>

\subsection{The Benchmarks}
In our previous work \cite{roberts-and-co-ecoop-2019}, we evaluated the performance of transient type checks using 21 benchmarks. We started with the 14 benchmarks of the \AWFY
benchmark suite \cite{Marr2016}: Bounce, CD, DeltaBlue, GraphSearch, Havlak, Json, List, Mandelbrot, NBody, Permute, Richards, Sieve, Storage and Towers benchmarks. We added another nine benchmarks taken from the gradual-typing literature.
Our goal was to complement the \AWFY with additional ones that are used for similar experiments and can be ported to Grace.
We surveyed a number of papers
\citep{Takikawa2016,Vitousek2017,Muehlboeck2017,Bauman2017,Richards2017,Stulova2016,Greenman2018}
and selected additional benchmarks that have been used by multiple papers.
Two of these benchmarks (NBody and Sieve) overlapped with the \AWFY suite,
or were available in different versions.
While not always behaviourally equivalent,
we chose the \AWFY versions since we already used them to
establish a performance baseline.
The selected benchmarks as well as the papers in which they were used are shown in
Table~\ref{tab:gradual-benchmarks}.

>>>>

\subsection{The Benchmarks}
In our previous work \cite{roberts-and-co-ecoop-2019}, we evaluated the performance of transient type checks using 21 benchmarks. We started with the 14 benchmarks of the \AWFY
benchmark suite \cite{Marr2016}: Bounce, CD, DeltaBlue, GraphSearch, Havlak, Json, List, Mandelbrot, NBody, Permute, Richards, Sieve, Storage and Towers benchmarks. We added another \ugh{nine}\sm{14 plus 9 isn't 21} benchmarks taken from the gradual-typing literature.\sm{it's also unclear whether this is about previous work or what we do now.}
Our goal was to complement the \AWFY with additional ones that are used for similar experiments and can be ported to Grace.
We surveyed a number of papers
\citep{Takikawa2016,Vitousek2017,Muehlboeck2017,Bauman2017,Richards2017,Stulova2016,Greenman2018}
and selected additional benchmarks that have been used by multiple papers.
Two of these benchmarks (NBody and Sieve) overlapped with the \AWFY suite,
or were available in different versions.
While not always behaviourally equivalent,
we chose the \AWFY versions since we already used them to
establish a performance baseline.
The selected benchmarks as well as the papers in which they were used are shown in
Table~\ref{tab:gradual-benchmarks}.
\sm{this paragraph needs to be cleaned up.
We need to say what we use now. Clearly, and not intermingled with previous work.
And then, afterwards we can say whether this is the same we did before. or how it differs.
}
